Advances in Artificial Intelligence for Data Visualization: Automated Reading of Residual Plots with Computer Vision

### 2023-04-18 Milestone_presentation_2/Milestone_presentation_2/Untitled.Rmd
simulate residuals

>>>>

.center[
# 🎲Simulate Residuals from the Assumed Model🎲
]

Data used in the $m − 1$ null plots needs to be simulated.

For classical normal linear regression model, the **residual rotation** technique (Buja, et al. 2009) can be applied:

<p> 1. Generate independent random draws \(w_i, i=1,...,N\) from \(N(0, 1)\). </p>

<p> 2. Regress \(w\) on \(x\) and obtain the residuals \(r_i, i=1,...,N\). </p>

<p> 3. Rescale \(r_i\) by \(\sqrt{RSS_{old}/RSS_{new}}\) to obtain the simulated residuals, where \(RSS_{old}\) is the residual sum of square of the original regression, and \(RSS_{new}\) is the residual sum of square of the regression fitted on step 2. </p>
